Universal Anonymous Signatures

### 2022-07-04 prism-backend/research/gsac/app-related-proofs.tex
More missing files.

\section{\UAS-Based Instantiations of Related Schemes}
\label{app:related-models}

In the following subsections we reproduce models of related schemes in the
literature. Then, we give concrete \fissue, \feval and \finsp functions that
make \UAS mimic their functionality. Finally, we prove for each case that
\UAS -- restricted with the corresponding functions -- indeed meets their
security models, thus proving that \UAS is a generalization of all of them.

\subsection{Group Signatures}
\label{sapp:related-models-gs}

We adopt the model in \cite{bsz05}. In this abstraction
of group signatures, the opener returns an index uniquely identifying the group
member that created a signature, along with a correctness proof. For ease of
exposition, assume that, w.l.o.g., this index is just the public key that the
group member chooses when joining the group\footnote{The user public key is
  assumed to be accessible from a public table in \cite{bsz05}, so it is direct
  to translate the public key into an index, if needed.}. A group signature
scheme, according to \cite{bsz05}, is composed of $KeyGen$, \UKeyGen, \Sign,
\Verify, \Open and \Judge algorithms, as well as an $\langle\Obtain,\Issue
\rangle$ interactive protocol. Their description is very similar to that of
\GSAC, so we refer to \cite{bsz05} for detailed descriptions. For ease of
reference, we replicate the security games in \figref{fig:model-gs}.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.45\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,gs}(1^\secpar)$}{%
        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
        d \gets \adv^{\mathcal{O}^{anon}}(\gpk,\isk) \\
        \pcreturn d 
      }

      \vspace*{5em}

      \procedure[linenumbering]{$\Exp^{frame}_{\adv,gs}(1^\secpar)$}{%
        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
        (\msg,\sig,\upk,\tau) \gets \adv^{\mathcal{O}^{frame}}
        (\gpk,\osk,\isk) \\
        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
        \pcreturn 1~\pcif \upk \in \HU \land \PRVUK[\upk] \neq \bot \land
        \Judge(\gpk,\upk,\msg,\sig,\tau) = 1~\land \\
        \pcind \adv~\textrm{did not query}~USK(\upk)~\textrm{or}~
        GSig(\PRVUK[\upk],\msg) \\
        \pcreturn 0
      }       
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.55\textwidth}
      \procedure[linenumbering]{$\Exp^{trace}_{\adv,gs}(1^\secpar)$}{%
        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
        (\msg,\sig) \gets \adv^{\mathcal{O}^{trace}}(\gpk,\osk) \\
        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
        (\upk, \tau) \gets \Open(\gpk,\osk,\trans,\msg,\sig) \\
        \pcif \upk \notin \HU \cup \CU \lor \Judge(\gpk,\upk,\msg,\sig,\tau)
        = 0: \\ 
        \pcind \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for group signatures \cite{bsz05}, only with minor    
    ``harmless'' edits to compare easier with \CUASGS. Concretely, since we
    output {\upk}s instead of indexes, $i=0$ in the traceability game now reads
    $\upk \notin \HU \cup \CU$. For the oracles' definitions, check the
    referenced paper.
    $\mathcal{O}^{anon} \gets \lbrace Ch,Open,SndToU,WReg,USK,CrptU \rbrace$,
    $\mathcal{O}^{trace} \gets \lbrace SndToI,AddU,RReg,GSig,USK,CrptU \rbrace$,
    and $\mathcal{O}^{frame} \gets \lbrace SndToU,WReg,GSig,USK,CrptU \rbrace$.
  }
  \label{fig:model-gs}  
\end{figure}

\subsubsection{\CUASGS construction.} %
We show that, as specified in \tabref{tab:uas-alt-funcs}, our \CUASGen
construction for \UAS, restricted to $\fissue^1$ as issuance function,
$\feval^0$ as signature evaluation function, and $\finsp^{\upk}$ as opening
function, is a secure group signature scheme according to the \cite{bsz05}
model. We first quickly define the algorithms, and then prove security.

\begin{description}
\item[$(\gpk,\isk,\osk) \gets KeyGen(1^\secpar)$.] Runs the \Setup algorithm
  of \CUASGen, and one instance of \IKeyGen and \OKeyGen. Assigns the public
  keys to \gpk.
\item[$(\upk,\usk) \gets \UKeyGen(1^\secpar)$.] Runs \UKeyGen from \CUASGen, and
  computes $\CCommit(\usk;0)$ as \upk.
\item[$\langle \cred,\utrans \rangle \gets
  \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Runs $\langle\Obtain,
  \Issue\rangle$ as in \CUASGen, with $\attrs \gets \emptyset$. Note that, to
  constraint to only one credential per user, it suffices to require the user
  to prove that the ``randomness'' it uses when committing to its private key
  is actually $0$, and check whether the received commitment has been seen
  before. For details, see the BBS+ instantiation of the underlying \SBCM
  building block in \secref{sapp:sbcm}.
\item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
  runs $(\sig,0) \gets \Sign(\usk,\opk,\cred,\msg,\feval^0)$ from \CUASGen.
  Simply returns \sig.
\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
  returns whatever $\Verify(\opk,\ipk,\sig,0,\msg,\feval^0)$ from \CUASGen
  outputs.
\item[$(\upk,\pi) \gets \Open(\gpk,\osk,\trans,\sig,\msg)$.] Parses \gpk as
  $(\ipk,\opk)$, and returns whatever \CUASGen outputs in $\Open(\osk,\ipk,\sig,
  0,\msg,\feval^0)$. Note that, internally, the latter call to \Open runs
  $\finsp^{\upk}$, where $\upk = \CCommit(\usk;0)$, just as proved in $\langle
  \Obtain,\Issue\rangle$.
\item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Parses \gpk as $(\ipk,
  \opk)$, and returns whatever \CUASGen outputs in $\Judge(\opk,\upk,\pi,\sig,
  0,\msg)$.
\end{description}

\paragraph{Security of \CUASGS.} %
We prove that our \CUASGS construction is a secure group signature scheme,
according to \cite{bsz05}, if the underlying \CUASGen construction is secure.

@@

\subsection{Group Signatures with Message Dependent Opening}
\label{sapp:related-models-gsmdo}

We cannot build the exact same functionality, nor follow the exact same security
model as in the group signatures with message dependent opening (GS-MDO) scheme
described in \cite{ehk+19}. Simply because, therein, the opening functionality
is divided in two authorities: the admitter, who decides which messages are
subject to be opened or not, and generates a token that enables opening
signatures over such messages; and the opener, who performs the actual opening,
but cannot do it without the tokens generated by the admitter. Intuitively, this
can be seen as a sort of ``distribution'' of the opening capability. We define
a variant of this model in which the admitter and opener are combined back into
one entity (the opener), who can only open signatures over predefined messages,
but cannot open any other signature. Moreover, our variant directly supports the
scenario of multiple such openers, each being able to open only signatures
over different messages. Note that it would not be hard to apply thresholding
techniques to extend this case so that our ``unified'' opener role is shared
across multiple entities, who have to cooperate in order to open a signature
\needcite, thus achieving something very close ``in spirit'' to the scheme in
\cite{ehk+19}. In addition, while \cite{ehk+19} follows the static group
signature setting, we move to the dynamic one. Informally, our variant of GS-MDO
is composed of the following algorithms: \Setup,
\IKeyGen, \OKeyGen, \UKeyGen, \Sign, \Verify, \Open; as well as the $\langle
\Obtain, \Issue \rangle$ interactive protocol. \OKeyGen generates an opening
key pair which is already configured to open signatures only over some fixed
(but arbitrary) set of messages. The remaining algorithms are as usual, so we
defer a more detailed description to the construction. The oracles are the same
as in \UAS. The resulting security model is given in \figref{fig:model-gsmdo},
which we adapt from \cite{ehk+19}.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.45\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,gsmdo}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\ipk,\isk) \gets \IKeyGen(\parm) \\
        b^* \gets \adv^{\mathcal{O}^{anon}}(\parm,\ipk) \\
        \pcreturn b^*
      }

      \vspace*{5em}

      \procedure[linenumbering]{$\Exp^{frame}_{\adv,gsmdo}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\ipk,\isk) \gets \IKeyGen(\parm) \\
        (\msg,\sig,\upk,\tau) \gets \adv^{\mathcal{O}^{frame}}
        (\ipk,\isk) \\
        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
        \pcreturn 1~\pcif \upk \in \HU \land \PRVUK[\upk] \neq \bot \land
        \Judge(\gpk,\upk,\msg,\sig,\tau) = 1~\land \\
        \pcind \adv~\textrm{did not query}~USK(\upk)~\textrm{or}~
        GSig(\PRVUK[\upk],\msg) \\
        \pcreturn 0
      }       
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.55\textwidth}
      \procedure[linenumbering]{$\Exp^{trace}_{\adv,gsmdo}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\ipk,\isk) \gets \IKeyGen(\parm) \\
        (\msg,\sig,\upk,\tau) \gets \adv^{\mathcal{O}^{trace}}
        (\ipk,\opk,\osk) \\
        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
        (\upk, \tau) \gets \Open(\gpk,\osk,\trans,\msg,\sig) \\
        \pcif \upk \notin \HU \cup \CU \lor \Judge(\gpk,\upk,\msg,\sig,\tau)
        = 0: \\ 
        \pcind \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for our GS-MDO variant.
    $\mathcal{O}^{anon} \gets \lbrace \OGEN^{\smsg},\HUGEN,\CUGEN,\WREG,
    \OBTAIN,\SIGN,\OPEN,\CHALb \rbrace$; $\mathcal{O}^{trace} \gets \lbrace
    \OGEN,\HUGEN,\CUGEN,\ISSUE,\OBTISS,\RREG,\SIGN \rbrace$;
    $\mathcal{O}^{frame} \gets \lbrace \OGEN,\HUGEN,\CUGEN,\WREG,
    \OBTAIN,\SIGN \rbrace$. $\OGEN^{\smsg}$ is like \OGEN, but only accepting
    functions of type $\finsp^{\smsg}$.
  }
  \label{fig:model-gsmdo}  
\end{figure}

\subsubsection{\CUASGSMDO construction.} %
We show that, as specified in \tabref{tab:uas-alt-funcs}, our \CUASGen
construction for \UAS, restricted to $\fissue^1$ as issuance function,
$\feval^0$ as signature evaluation function, and $\finsp^{\smsg}$ as opening
function, is a secure group signature scheme with message dependent opening
as modelled in \figref{fig:model-gsmdo}. We first quickly define the algorithms,
and then prove security.

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.] Like in vanilla \CUASGen.
\item[$(\upk,\usk) \gets \UKeyGen(1^\secpar)$.] Like the \UKeyGen function for
  \CUASGS, in \secref{sapp:related-models-gs}.
\item[$\langle \cred,\utrans \rangle \gets
  \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Like the corresponding
  protocol in in vanilla \CUASGS, \secref{sapp:related-model-gs}.
\item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Like in vanilla \CUASGen, limited
  on evaluation functions $\feval^0$ and opening functions $\finsp^{\smsg}$.
\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Like in vanilla \CUASGen.
\item[$(\upk,\pi) \gets \Open(\gpk,\osk,\trans,\sig,\msg)$.] Like in vanilla
  \CUASGen.
\item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Like in vanilla \CUASGen.
\end{description}

\paragraph{Security of \CUASGSMDO.} %
Our \CUASGSMDO construction is a secure group signature scheme,
according to the model in \figref{fig:model-gsmdo}, if the underlying \CUASGen
construction is secure.

Note that both  model construction are essentially restrictions to the model
and construction of \CUASGen. Thus, security directly follows from security of
\CUASGen.

% \begin{theorem}[Anonymity of \CUASGSMDO]
%   If the base \CUASGen construction is anonymous according to
%   \defref{def:anonymity-uas}, then \CUASGSMDO is an anonymous group signature
%   scheme.
% \end{theorem}

% \begin{proof}

%   \qed
% \end{proof}

% \begin{theorem}[Traceability of \CUASGSMDO]
%   If the base \CUASGen construction has unforgeable signing according to
%   \defref{def:sign-forge-uas}, then \CUASGSMDO is a traceable group signature
%   scheme.
% \end{theorem}

% \begin{proof}
%   Traceability follows directly from the corresponding proof for \CUASGS.
%   \qed
% \end{proof}

% \begin{theorem}[Non-frameability of \CUASGSMDO]
%   If the base \CUASGen construction is non-frameable according to
%   \defref{def:frame-uas}, then \CUASGSMDO is a non-frameable group signature
%   scheme.
% \end{theorem}

% \begin{proof}
%   Non-frameability follows directly from the corresponding proof for \CUASGS.
%   \qed
% \end{proof}

\subsection{Ring Signatures}
\label{sapp:related-models-rs}

We adopt the model in \cite{bkm06}, where security of ring signatures is
defined according to the games in \figref{fig:model-rs}. A ring signature
scheme consists of three algorithms $(KeyGen,Sign,Verify)$. Roughly,
$((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar)$ produces $n$
signing key pairs, $\sig \gets Sign(\sk_i,R,\msg)$ creates a signature for
anonymity set $R \subseteq \lbrace \pk_1, \dots, \pk_t \rbrace$, using secret
key $\sk_i$, associated to some $\pk_i \in R$; and $1/0 \gets Verify(R,\sig,
\msg)$ checks if \sig is a valid signature over \msg for ring $R$.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.55\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,rs}(1^\secpar)$}{%
        ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
        (i_0,i_1,R,\msg,\st) \gets \adv^{SIGN}(\pk_1,\dots,\pk_n) \\
        \pcif % R \not\subseteq \lbrace [n] \rbrace \lor
        \lbrace \pk_{i_0},\pk_{i_1} \rbrace \notin R \lor %\\
        i_0 = i_1: \pcreturn \bot \\
        \sig \gets Sign(\sk_{i_b},R,\msg)) \\
        b^* \gets \adv(\sig,\st) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.5\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,rs}(1^\secpar)$}{%
        ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
        (R,\sig,\msg) \gets \adv^{SIGN,CORR}(\pk_1,\dots,\pk_n) \\
        \pcif Verify(R,\sig,\msg) = 0: \pcreturn 0 \\
        \pcreturn 1~\pcif R \subseteq [n] \setminus CU = \emptyset~\land \\
        \pcind \adv~\textrm{never queried}~SIGN(\cdot,R,\msg) \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for ring signatures \cite{bkm06}. The SIGN oracle
    accepts a $(i,R,\msg)$ tuple, where $pk_i$ must be part of $R$, and
    returns $\sig \gets Sign(\sk_i,R,\msg)$. The oracle $CORR$ accepts an
    index $i$, and lets $\adv$ learn $\sk_i$. Corrupted user indexes are
    added to list $CU$.}
  \label{fig:model-rs}  
\end{figure}

Intuitively, a ring signature scheme $rs$ is anonymous if, for every p.p.t.
\adv, $|\Pr[\Exp^{anon-1}_{\adv,rs}(1^\secpar)] = 1| -
|\Pr[\Exp^{anon-1}_{\adv,rs}(1^\secpar)] = 0|$ is a negligible function of
$1^\secpar$; and a ring signature scheme $rs$ is unforgeable if, for every
p.p.t. \adv, the probability that $\Exp^{forge}_{\adv,rs}(1^\secpar)$ returns
$1$ is also negligible in $1^\secpar$. For short, we say that a ring signature
scheme meeting both anonymity and unforgeability as specified above, is a secure
ring signature scheme.

\subsubsection{\CUASRing Construction.} %
We show that, as specified in \secref{ssec:uas-ring}, our \CUASGen construction
for \UAS, with alternative NIZK relationship $\NIZKRel_{\Sign-prv}$ for signing,
issuance function $\fissue^{\sring}$, signature evaluation function
$\feval^{\attrs}$, and inspection function $\finsp^0$, is a secure ring
signature scheme. Thus, in this section, when we write \CUASGen, we refer to
its specific variant built from the previous modifications.

\begin{description}  
\item[$\parm \gets \Setup(\secpar,\AttrSpace)$.] As in \CUASGen, but using
  $\NIZKRel_{\Sign-prv}$ instead of $\NIZKRel_{\Sign}$.  
\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] As in \CUASGen, using
  $\fissue^{\sring}$.  
\item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp).$] As in \CUASGen, where every
  opener that wants to be a valid opener in \CUASRing, needs to set \finsp to
  $\finsp^0$.  
\item[$\usk \gets \UKeyGen(\parm).$] Can only be run after \IKeyGen. Let 
  $\usk \gets \isk$.
\item[$\langle \cred,\bot,\utrans,\bot \rangle \gets
  \langle \Obtain(\usk,\scred,\attrs),\Issue(\isk,\sipk,\attrs)\rangle.$]
  The user picks a ring from an (publicly) available list of issuers (users),
  i.e. $\sring \gets \lbrace \ipk_i \rbrace_{i \in [t]}$, for some $t$. Then,
  runs the $\langle \Obtain,\Issue \rangle$ protocol as in \CUASGen, acting both
  as user and as issuer, and using $\fissue^{\sring}$ as issuance function.
  \attrs are the public keys of the users (issuers) to be included in the ring.
\item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\scred,\msg,\feval).$] As in
  \CUASGen, using $\feval^{\attrs}$ as sign evaluation function, using
  as credential for signing the credential obtained in the desired $\langle
  \Obtain,\Issue \rangle$ session and, as \opk, any previously registered \opk
  (i.e., such that $\finsp=\finsp^0$).
\item[$1/0 \gets \Verify(\opk,\sipk,\sig,\yeval,\msg,\feval).$] As in \CUASGen.
  Note that $\sipk = \sring$, and $\feval=\feval^{\attrs}$.
\item[$\Open$ and $\Judge$.] As in \CUASGen. Note that $\finsp=\finsp^0$.
\end{description}

\todo{I guess we need to show that changing the NIZK for signing does not affect
  security. This leads to ``What are the conditions that need to be checked/cannot
  be altered in the default NIZK sign, that make \CUASGen secure?'' }

\paragraph{Security of \CUASRing.} %
We prove that our \CUASRing construction is anonymous and unforgeable, if
the underlying \CUASGen construction is secure.

@@

\subsection{Anonymous Credentials}
\label{sapp:related-models-ac}

We adopt the model in \cite{fhs19}, where security of anonymous credentials
(with selective disclosure). Therein, an anonymous credential scheme is
defined via $OrgKeyGen$ (which we rename to $IssKeyGen$, and $UserKeyGen$
algorithms (roughly equivalent to
\IKeyGen and \UKeyGen for \UAS), and $Obtain,Issue$ and $Show,Verify$
interactive protocols. The issuance interactive protocol is equivalent to
the issuance protocol in \UAS. Similarly, $Show,Verify$ is equivalent to
the interactive extension of \Sign and \Verify in \UAS, which we show how
to build in \secref{ssec:variants-gsac} (for \GSAC, but the case for \UAS is
equivalent). The security definitions rely on $HU, CU, ObtIss, Obtain, Issue,
Show$, and $LoR$ oracles, which are essentially equivalent to our \HUGEN,
\CUGEN, \OBTISS, \OBTAIN, \ISSUE, \SIGN, and \CHALb oracles. We refer to
\cite{fhs19} for the full details. For ease of reference, we summarize the
security definitions in \cite{fig:model-ac}, with inocuous adaptations to
make them more suitable for comparison with our definitions.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.5\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,ac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
        b^* \gets \adv^{HU,CU,Obtain,Show,LoR}(\isk) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.5\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,ac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
        (D,\st) \gets \adv^{HU,CU,ObtIss,Issue,Show}(\ipk) \\
        \langle \cdot,(b,\utrans) \rangle
        \gets \langle \adv(\st),\Verify(\ipk,D) \rangle \\
        \pcif b = 1 \land \nexists j~\suchthat~(\OWNR[j] \in \CU
        \land D \subseteq \ATTR[j]): \\% \forall j, \OWNR[j] \in \CU
        % \implies D \not\subseteq \ATTR[j]: \\
        \pcind \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for anonymous credentials with selective disclosure
    \cite{fhs19}. \OWNR and \ATTR tables are essentially as in
    \secref{ssec:model-uas}.}
  \label{fig:model-ac}  
\end{figure}

\subsubsection{\CUASAC Construction.} %
We show that, as specified in \tabref{tab:uas-alt-funcs}, our \CUASGen
construction for \UAS, restricted to $\fissue^1$ as issuance function,
$\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as opening
function, is a secure anonymous credential scheme according to the \cite{fhs19}
model. We first quickly define the algorithms, and then prove security. Note
that, for better alignment with \UAS, we add a common setup process which is
part of $IssKeyGen$ in \cite{fhs19}. The change is inocuous functionality- and
security-wise, though.

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\parm' \gets \Setup(1^\secpar)$
    and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our \CUASGen
    construction. Returns $\parm \gets (\parm',\opk)$.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \IKeyGen from our
  \CUASGen construction, setting $\fissue^1$ as issuance function.
\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \UKeyGen from the
  \CUASGen construction, and computes $\CCommit(\usk;0)$ as \upk.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
  $\fissue^1$ as issuance function.
\item[$\langle 1/0,((1,\utrans)/(0,\utrans)\rangle
  \gets \langle Show(\ipk,\attrs,\dattrs,
  \cred),\Verify(\ipk,\dattrs) \rangle$.]
  Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
  using $\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as
  open function, with \opk from \parm as opener public key.
\end{description}

\paragraph{Security of \CUASAC.} %
We prove that \CUASAC is an anonymous and unforgeable anonymous credential
scheme, according to \cite{fhs19}, if the underlying \CUASGen construction
is anonymous and has unforgeable signing. Note that issuance unforgeability
of \CUASGen is not needed, as the model in \cite{fhs19} does not allow
leveraging other credentials not any fixed custom issuance policy. Thus,
signature unforgeability from \UAS is enough. Note that AC schemes modelled
as in \cite{fhs19} do not have issuance anonymity, as the user public key
is passed to the issuer.

@@

\subsection{Delegatable Anonymous Credentials}
\label{sapp:related-models-dac}

We give a simple definition for a Delegatable Anonymous Credentials (DAC)
scheme, extending \cite{fhs19} and inspired by \cite{bcc+09}. Unlike the latter,
our simple scheme built from \CUASGen does not ensure privacy of the delegation
chain -- which could be achieved by making \feval output projective proofs like
in \cite{bcc+09}, but since our goal is to showcase the feasibility of building
DAC from \UAS, we leave that out for brevity. Our simple scheme does, however,
ensure that a (not top-level) issuer can only delegate attributes contained in a
credential it owns. Also, for simplicity, we restrict to the case of using one
credential per signature/interactive credential presentation, and assume that
all parties use the same opener and \finsp function.
%
The functionality is thus defined as in \appref{sapp:related-models-ac}, i.e.,
we have $Setup$, $IssKeyGen$ and $UserKeyGen$ algorithms, and $\langle Obtain,
Issue \rangle$ and $\langle Show,Verify \rangle$ interactive protocols.
%
In the modelling for this setting, since there are multiple issuers, in addition
to the oracles in \appref{sapp:related-models-ac}, we use $HI$ and $CI$ oracles,
equivalent to \IGEN and \ICORR in our \UAS model, which allow adding honest
issuers, and corrupt existing ones, respectively. The issuance and sign
anonymity properties are as before. For unforgeability, we still require
that no adversary can authenticate using a set of attributes that have not been
issued to a corrupt user. In addition, we require that for any possible
successful authentication protocol using a level-$n$ credential, we can extract
a chain of credentials of length $n$ such that each level-$i$ credential can
be used successfully to authenticate a level-$(i+1)$ credential up to the
level-$n$ credential, and that the attributes revealed in the level-$n$
authentication are contained in all the credentials up the chain.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.45\textwidth}
      \procedure[linenumbering]{$\Exp^{iss-anon-b}_{\adv,dac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        b^* \gets \adv^{\mathcal{O}_{iss-anon}}(\parm) \\
        \pccomment{Abort if challenge creds belong to} \\
        \pccomment{users with different delegation chains} \\
        \pcreturn b^*
      }
      \vspace*{0.5em}

      \procedure[linenumbering]{$\Exp^{sig-anon-b}_{\adv,dac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        b^* \gets \adv^{\mathcal{O}_{sig-anon}}(\parm) \\
        \pccomment{Abort if challenge sigs belong to} \\
        \pccomment{users with different delegation chains} \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.55\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,dac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (D=(n,D'),\ipk_n,\st) \gets
        \adv^{\mathcal{O}_{forge}}(\parm) \\
        \langle\cdot,(b,\utrans)\rangle \gets
        \langle \adv(\st),\Verify(\ipk_n,D)\rangle \\
        \pcif b = 0: \pcreturn 0 \\
        \pcif \nexists j~\suchthat~(\OWNR[j] \in \CU
        \land D \subseteq \ATTR[j]): \pcreturn 1 \\        
        (ipk_0, \lbrace (\ipk_i,\cred_i) \rbrace_{i \in [1,n]})
        \gets ExtractChain(\utrans) \\ 
        \pcif \exists i \in [1,n]~\suchthat~
        \iid = \ISR[\ipk_{i-1}] \notin \CI~\land \\
        \pcind D' \not\subseteq \ATTR[\iid]) \land
        D' \subseteq \ATTR[\ISR[\ipk_i]]: \\
        \pcind \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for delegatable anonymous credentials with selective
    disclosure based on \cite{fhs19}. $\mathcal{O}_{iss-anon} \gets \lbrace HU,
    CU,HI,CI,Obtain,Issue,ObtIss,Show,IssLoR\rbrace$, $\mathcal{O}_{sig-anon}
    \gets \lbrace HU,CU,HI,CI,Obtain,Issue,ObtIss,Show,SigLoR\rbrace$.
    $\mathcal{O}_{forge} \gets \lbrace HU,CU,HI,CI,Obtain,ObtIss,Issue,Show
    \rbrace$. $IssLor$ is equivalent to \OBTCHALb in \UAS, whereas $SigLor$ is
    equivalent to \CHALb. Also, \OWNR and \ATTR tables are essentially as in
    \secref{ssec:model-uas}. $\ISR[\ipk]$, in this case, returns the identifier
    of the issuer with public key \ipk. With $D =
    (n,D')$ we mean that the first attribute in the revealed set $D$ is $n$,
    which denotes the level of the credential used for authentication.}
  \label{fig:model-dac}  
\end{figure}

\subsubsection{\CUASDAC Construction.} %
In a delegatable AC (DAC) scheme, all users are (or may be) also issuers. We
only distinguish between top-level issuers, who have level $n=0$, and
lower-level issuers, who have level $n>0$. In our \CUASDAC scheme, we assume
that the first attribute (after the user's secret key) encodes the level of
the credential. That is, $\attrs_1=n$, for a credential of level $n$. In
addition, all users (i.e., with $n>0$) who want to delegate have to publicly
list:

\begin{enumerate}
\item The level $n$ of the credential they delegate.
\item Their public key \ipk.
\item An \UAS signature proving knowledge of a credential of level $n$, and over
  the attributes that this level-$n$ issuer is delegating.
\item The \ipk of the parent issuer.
\item The $\fissue^{n,\dattrs}$ function they will require for delegating.
\item An $\feval^{n,\dattrs}$ function used to produce the signature at item 2.
\end{enumerate}

We assume that, from an \ipk, it is possible to find the corresponding issuer
(e.g., using the previously mentioned public list). The mentioned
$\fissue^{n,\dattrs}$ functions must follow the pattern in \esref{eq:funcs-dac}.
Namely, the issuance function checks that the first requested attribute equals
$n+1$, and that all requested attributes are a subset of the attribute set
\dattrs being delegated by the level-$n$ issuer. In addition, signature
evaluation functions $\feval^{n,\dattrs}$, also shown in \esref{eq:funcs-dac},
must reveal the level of the credential used to produce the \UAS signature at
item 2, as well as the set of attributes \dattrs that the level-$n$ issuer
delegates. Verifiers can then trivially check if the set of revealed attributes
are contained within the attributes delegatable by the parent issuer%
\footnote{Additional checks may be added in both functions, but this is
  the bare minimum.}. \figref{fig:XXX} depicts a sample of the delegation chain
that this structure creates.

\begin{align}
  & \fissue^{n,\dattrs}(\usk,\cred,\attrs) \coloneqq \lbrace
    \pcif \attrs_1 = n+1 \land \attrs \subseteq \dattrs: \pcreturn 1; \pcelse \pcreturn 0
    \rbrace \nonumber \\
  & \feval^{n,\dattrs}(\usk,\cred,\msg) \coloneqq \lbrace
    \pcreturn (\attrs_1(\cred),\dattrs(\cred)) \rbrace
  \label{eq:funcs-dac}
\end{align}

From this high-level description, we define the algorithms of \CUASDAC:

>>>>

\section{Proofs for Relationships with Other Schemes}
\label{app:related-proofs}

\subsection{Security of \CUASGS}

We prove that our \CUASGS construction is a secure group signature scheme,
according to \cite{bsz05}, if the underlying \CUASGen construction is secure.

@@

\subsection{Security of \CUASRing}

We prove that our \CUASRing construction is anonymous and unforgeable, if
the underlying \CUASGen construction is secure.

@@

\subsection{Security of \CUASAC}

We prove that \CUASAC is an anonymous and unforgeable anonymous credential
scheme, according to \cite{fhs19}, if the underlying \CUASGen construction
is anonymous and has unforgeable signing. Note that issuance unforgeability
of \CUASGen is not needed, as the model in \cite{fhs19} does not allow
leveraging other credentials not any fixed custom issuance policy. Thus,
signature unforgeability from \UAS is enough. Note that AC schemes modelled
as in \cite{fhs19} do not have issuance anonymity, as the user public key
is passed to the issuer.

@@

\subsection{Security of \CUASDAC}

We prove that \CUASDAC is an anonymous and unforgeable DAC scheme, according to
the model in \figref{fig:model-dac}, if the underlying \CUASGen construction has
anonymous issuance and signing, and has unforgeable issuance and signing.
